The watershed transform in ITK - discussion and new developments

### 2006-04-24 article/Article.tex
change the size of some image
darcs-hash:20060424071352-2fc9d-a080b596340c797115623aa946abc365d8b48028.gz

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=4]{threshold}}
\subfigure[No minima threshold]{\includegraphics[scale=4]{threshold00-rgb}}
\subfigure[Minima threshold = 10]{\includegraphics[scale=4]{threshold10-rgb}}
\subfigure[Minima threshold = 20]{\includegraphics[scale=4]{threshold20-rgb}}
\subfigure[Minima threshold = 30 and Minima threshold = 40]{\includegraphics[scale=4]{threshold30-rgb}}
\subfigure[Minima threshold = 50]{\includegraphics[scale=4]{threshold50-rgb}}
\subfigure[markers]{\includegraphics[scale=4]{threshold-markers}}
\subfigure[Watershed from markers]{\includegraphics[scale=4]{threshold-markersMf-rgb}}
\caption{Different results of watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical watershed over segmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image. All the watersheds were performed with $MarkWatershed = true$ and $FullyConnected = false$.}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=4]{threshold}}
\subfigure[No minima threshold]{\includegraphics[scale=4]{threshold00-itk-rgb}}
\subfigure[Minima threshold = 10]{\includegraphics[scale=4]{threshold10-itk-rgb}}
% \subfigure[Minima threshold = 20]{\includegraphics[scale=4]{threshold20-itk-rgb}}
\subfigure[Minima threshold = 40]{\includegraphics[scale=4]{threshold40-itk-rgb}}
\subfigure[Minima threshold = 63]{\includegraphics[scale=4]{threshold63-itk-rgb}}
\subfigure[Minima threshold = 65]{\includegraphics[scale=4]{threshold65-itk-rgb}}
\subfigure[markers]{\includegraphics[scale=4]{threshold-markers}}
\subfigure[Watershed from markers]{\includegraphics[scale=4]{threshold-markers-itk-rgb}}
\caption{Different results of watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical watershed over segmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image..}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=3.2]{threshold}}
\subfigure[No minima threshold]{\includegraphics[scale=3.2]{threshold00-rgb}}
\subfigure[Minima threshold = 10]{\includegraphics[scale=3.2]{threshold10-rgb}}
\subfigure[Minima threshold = 20]{\includegraphics[scale=3.2]{threshold20-rgb}}
\subfigure[Minima threshold = 30 and Minima threshold = 40]{\includegraphics[scale=3.2]{threshold30-rgb}}
\subfigure[Minima threshold = 50]{\includegraphics[scale=3.2]{threshold50-rgb}}
\subfigure[markers]{\includegraphics[scale=3.2]{threshold-markers}}
\subfigure[Watershed from markers]{\includegraphics[scale=3.2]{threshold-markersMf-rgb}}
\caption{Different results of watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical watershed over segmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image. All the watersheds were performed with $MarkWatershed = true$ and $FullyConnected = false$.}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=3.2]{threshold}}
\subfigure[No minima threshold]{\includegraphics[scale=3.2]{threshold00-itk-rgb}}
\subfigure[Level = 0.1]{\includegraphics[scale=3.2]{threshold10-itk-rgb}}
% \subfigure[Level = 0.2]{\includegraphics[scale=3.2]{threshold20-itk-rgb}}
\subfigure[Level = 0.4]{\includegraphics[scale=3.2]{threshold40-itk-rgb}}
\subfigure[Level = 0.63]{\includegraphics[scale=3.2]{threshold63-itk-rgb}}
\subfigure[Level = 0.65]{\includegraphics[scale=3.2]{threshold65-itk-rgb}}
\subfigure[markers]{\includegraphics[scale=3.2]{threshold-markers}}
\subfigure[Watershed from markers]{\includegraphics[scale=3.2]{threshold-markers-itk-rgb}}
\caption{Different results of watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical watershed over segmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image..}
\end{center}
\end{figure}
